### 2015-02-21 appendices.tex
more SQL updates, new sql file
reworked the end of chapter 2 moved stuff to Appendix A

%%\section{Example Graphics}

%%\begin{figure}[h!]
%%\scriptsize
%%$$
%%\begin{array}{cc}
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
%%(a) & (b) \\
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
%%(c) & (d) \\
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
%%(e) & (f) \\
%%\end{array}
%%$$
%%\caption{A graphic in the appendix}
%%\end{figure}

%% Prints all figures and tables on the page and begins a new page
%% http://www.astro.rug.nl/~kuijken/latex.html
%%\clearpage

@@

>>>>

\section{Detailed Steps of the SDLC}
\label{app:detailedSDLC}

    Often times the SDLC contains more than the 5 basic steps of requirements, design,
    implementation, testing, and  deployment/maintenance.  Those are the high-level
    phases, but many steps are required to complete each phase.  The following list
    provides a more detailed version of what needs to be accomplished in the 
    entire life cycle of software development. These steps do not need 
    to occur in a sequential fashion.

    \begin{easylist}[itemize]
        & Identify the Work/Task/Project
        && Get Initial Idea 
        && Obtain Details
        & Estimate
        && Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
        && Obtain Approval 
        && Quit or Go Forward
        & Document Requirements
        && Identify the Requirements
        && Detail the Requirements
        & Design The Software
        && Find System Integrations
        && Identify Functional Specs
        && Detail the Functional Specs
        & Development of all the tasks in Design and Requirements
        && Identify the Coding Tasks
        && Write the Code/Develop the solution
        && Write the Unit Tests
        & Test
        && Create Test Plans and Cases
        && Run Test Plans and Cases
        & Deployment
        && Create Deployment Steps
        && Run Deployment Steps
        & Maintenance
        && Capture Bugs
        && Survey Users
        & Start Again
    \end{easylist}

@@

\subsection{SQL CODE - FINAL SCORE TABLES}
    \lstinputlisting[language=SQL, label=src:overallscoreSQL]{source/overall_score_tables.sql}

### 2015-02-21 paper_10_intro.tex
reworked the end of chapter 2 moved stuff to Appendix A

>>>>

\subsection{TERMINOLOGY}
    Like any other business domain, the software engineering field has number
    of specific terms.  Many of these terms will be used throughout the remainder
    of the document, so definitions are provided.

    \begin{description}

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release
        \item[SIT]   (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
        \item[UAT]   (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occured for
            UAT, the software system is ready to proceed to production
        \item[PROD]  (Production) - The software has been released to the final audience.
        \item[defect] ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed test cases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

### 2015-02-21 paper_20_sdo.tex
reworked the end of chapter 2 moved stuff to Appendix A

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        many ommonalities exist among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the Implemenation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a roadmap for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development lifecycle.
        \end{description}

The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.

\begin{easylist}[itemize]
    & Identify the Work/Task/Project
    && Get Initial Idea 
    && Obtain Details
    & Estimate
    && Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
    &&Obtain Approval 
    && Quit or Go Forward
    & Document Requirements
    && Identify the Requirements
    && Detail the Requirements
    & Design The Software
    && Find System Integrations
    && Identify Functional Specs
    && Detail the Functional Specs
    & Development of all the tasks in Design and Requirements
    && Identify the Coding Tasks
    && Write the Code/Develop the solution
    && Write the Unit Tests
    & Test
    && Create Test Plans and Cases
    && Run Test Plans and Cases
    & Deployment
    && Create Deployment Steps
    && Run Deployment Steps
    & Maintenance
    && Capture Bugs
    && Survey Users
\end{easylist}

@@

\subsection{TERMINOLOGY}

\begin{description}

    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
    \item[Release] - A collection of projects being put in production on a specified date
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] ``A software defect is a bug or error that causes
                software to either stop operating or to produce
                invalid or unacceptable results'' as quoted from
            \cite{Jones2009}.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

              Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
\end{description}

Check these book \cite{Jones2009, Jones1996, Lee2003}.

>>>>

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        many commonalities exist among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the implementation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a roadmap for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development life cycle.
        \end{description}

        These 5 steps cannot cover everything that needs to be accomplished
        during a project.  They just provide of rough guideline of what needs
        to be completed in order to ensure a more successful software release.
        Appendix \ref{app:detailedSDLC} contains a more detailed list of the
        tasks necessary to complete the software life cycle.

@@

### 2015-02-21 paper_40_mpi.tex
reworked the end of chapter 2 moved stuff to Appendix A

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data.

            \paragraph{ALTERNATE APPROACH}
                The best possible score should be achieved
                when meeting the estimated date exactly.  The maximum score
                should come from the best estimate.  Then given historical
                release data, it is easy to determine an 
                average $\Delta$ between the actual and the estimated.  
                Finishing a project within that $\Delta$ should result 
                in a positive score.  Outside the $\Delta$ results in
                negative scores.  For example, a project releasing
                one day early or one day late would receive the same score
                because in both cases the estimate was missed by one day.

@@

                \begin{displaymath}
                   S_{4_i} = \left\{
                     \begin{array}{lr}
                        \text{where } \Delta_i \geq 1 & : -1 \times 100 \\
                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times 100  \\
                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times 100
                     \end{array}
                   \right] \text{   , calculate schedule score for each project $i$}
                \end{displaymath}

                \[
                    S_{4} = \frac{\sum^n_{i=1} S_{4_i}}{n} \text{   , average the schedule scores}
                \]
                \begin{itemize}
                    \item $n$ is the number of projects
                    \item $F_{a_i}$ the actual finish date of project i
                    \item $F_{s_i}$ the scheduled finish date of project i
                    \item $B_{s_i}$ the scheduled beginning date of project i
                    \item $\Delta_i$ the percent the schedule was missed
                    \item $\bar{\Delta}$ is the average percent RT misses schedules, $\approx 26$
                    \item $S_{4_i}$ is the schedule score for project $i$
                \end{itemize}

%The score can be accomplished with the following 
%algorithm.
%\[
%    S_4 = \frac{\sum^n_{i=1} \left( C_{a_i} - C_{e_i} \right)}{n}
%\]
%\begin{itemize}
%\item $C_a$ actual number of days for application $i$
%\item $C_e$ estimated number of days for application $i$
%\end{itemize}

        \subsubsection{REQUIREMENTS}

@@

                    Application ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Requirements Scheduled & Integer & Required \\
                    \myrowcolour%
                    Actual Requirements Released & Integer  & Required \\

>>>>

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data.  The exact distribution is needed for the Cumulative
                Distribution Function (C.D.F.).  The C.D.F. will be transformed to create
                the schedule score for MPI. Since all C.D.F. functions fall within the
                range $[0,1]$, the function needs to be shifted to center around 0, and then
                doubled to fill the desired range of $[-1,1]$. Thus the MPI schedule score
                for each project becomes the following.

                \[
                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
                \]

                Then the overall schedule score is calculated as below.

                \[
                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]

            \paragraph{ALTERNATE APPROACH}
                An alternative approach for scoring schedule goes as follows.
                The best possible score should be achieved
                when meeting the estimated date exactly.  The maximum score
                should come from the best estimate.  Then given historical
                release data, it is easy to determine an 
                average $\Delta$ between the actual and the estimated.  
                Finishing a project within that $\Delta$ should result 
                in a positive score.  Outside the $\Delta$ results in
                negative scores.  For example, a project releasing
                one day early or one day late would receive the same score
                because in both cases the estimate was missed by one day.

@@

                \begin{displaymath}
                   S_{4_i} = \left\{
                     \begin{array}{lr}
                        \text{where } \Delta_i \geq 1 & : -1 \times k \\
                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times k  \\
                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times k
                     \end{array}
                   \right] \text{   , calculate schedule score for each project $i$}
                \end{displaymath}

                \[
                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1 \text{   , average the schedule scores}
                \]
                where
                \begin{itemize}
                    \item $n$ is the number of projects
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the percent the schedule was missed
                    \item $\bar{\Delta}$ is the average percent schedules are missed
                    \item $S_{4_i}$ is the schedule score for project $i$
                \end{itemize}
                Again, this was just an alternate approach to scoring schedule.  It will not be used
                in the case studies.

        \subsubsection{REQUIREMENTS}
            The requirements of a software development organization are important.

@@

                    Project ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Requirements Scheduled & Integer & Required \\
                    \myrowcolour%
                    Actual Requirements Released & Integer  & Required \\
